\chapter{Acknowlodgements}

I gratefully thank Prof. Fred Hamprecht for the supervision of my thesis and the trust in my
work. Throughout my time at the HCI, I was able to work freely on cell tracking projects and,
whenever necessary, could visit Prof. Fred Hamprecht's office to discuss open questions and get
valuable input for the formulation of the proposed methods.

On my own (embryo-)genesis from research assistant to the completion of my thesis, I have met
exceptional people, both in skill and character. In addition to their extraordinary skills, all
group members gave me a warm welcome and always made me feel part of the team.

When I first started as a research assistant, Bernhard Kausler was my first mentor and introduced me
to the ``chain graph'' cell tracking method~(\cref{subsec:fg-chaingraph}). The lessons learned in
programming and mathematics laid the foundations for the successful completion of this
thesis. Furthermore, Bernhard Kausler remains a supportive adviser beyond our shared time at the
HCI. Equally important, Martin Schiegg made me part of the ``conservation'' cell tracking
project~(\cref{subsec:fg-conservation}) and made my thesis and the proposed methods possible. We
spent many days (and nights) in our common office tweaking and analyzing our cell tracking
methods. Without his exuberant support in mathematics and implementation, ``GMM for cell
reconstruction''~(\cref{cha:GMM}) and ``joint segmentation and tracking''~(\cref{cha:joint}) would
not have been possible.

In the process of writing the thesis I could rely on helpful and constructive comments on the
contents as well as on the layout and design of the thesis. I want to thank, in alphabetic order,
Anna Kreshuk, Bernhard Kausler, Carsten Haubold, Frederick Blumenthal, Gregor Urban, Martin Schiegg,
Melih Kandemir, Robert Walecki, Thorben Kr\"oger and Thorsten Beier for pointing out inconsistencies
in the manuscript before any reader could find them.  Furthermore, I would like to thank Christoph
Klein for his help with the manual evaluation of the proposed ``joint segmentation and tracking''
method.

All members of the Multidimensional Image Processing Group widened my knowledge in many ways and
added to the great time I had at the
HCI. I want to thank all of them in alphabetic order, namely
Anna Kreshuk,
Bernhard Kausler,
Buote Xu,
Bur\c{c}in Er\"ocal,
Carsten Haubold,
Chong Zhang,
Christoph Decker,
Christoph Straehle,
Ferran Diego,
Frank Herrmannsd\"orfer,
Frederick Blumenthal,
Gregor Urban,
Julian Yarkony,
Kemal Eren,
Luca Fiaschi,
Martin Schiegg,
Melih Kandemir,
Niko Krasowski,
Robert Walecki,
Stuart Berg,
Thorben Kr\"oger,
Thorsten Beier and
Ullrich K\"othe.
% Ullrich K\"othe,
% Bur\c{c}in Er\"ocal, Melih Kandemir, Chong Zhang, Ferran Diego, Thorsten Beier, Stuart Berg, Frederick
%Blumenthal, Christoph Decker, Kemal Eren, Luca Fiaschi, Carsten Haubold, Frank Herrmannsd\"orfer,
%Niko Krasowski, Anna Kreshuk, Thorben Kr\"oger, Christoph Straehle, Gregor Urban, Robert Walecki,
%Buote Xu and Julian Yarkony.
For their support in all administrative affairs, I would like to thank
Barbara Werner and Markus Nullmeier.

Finally, I thank my parents Ursula Prinzing-Hanslovsky and Paul Hanslovsky. Without their ongoing
support throughout all my studies and my final year in particular, this thesis would not have been
possible.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../main"
%%% End: 
